Lineage Analysis of CRISPR and shRNA Screens

### 2018-09-07 lineages_18Q3.Rmd

## D. Charytonowicz ell line converter

This comprehensive cancer cell line information curated by Daniel Charytonowicz.
```{r}
ccl_converter <- read.delim("./data_munging/cell_line_database_completed_extra_grouped_doids_FINAL.csv", sep = "\t", header = TRUE)
colnames(ccl_converter)[colnames(ccl_converter) == "ccle_cell_line_name"] <- "CCLE_Name"
colnames(ccl_converter)[colnames(ccl_converter) == "broad_id"] <- "Broad_ID"
```

```{r}
ccl_converter_test <- read.delim("./data_munging/cell_line_database_FINAL_MASTER.tsv", sep = "\t", header = TRUE)
colnames(ccl_converter_test)[colnames(ccl_converter_test) == "ccle_cell_line_name"] <- "CCLE_Name"
colnames(ccl_converter_test)[colnames(ccl_converter_test) == "broad_id"] <- "Broad_ID"
```

@@

```{r, include=FALSE}
dan_test <- select(ccl_converter, CCLE_Name, Broad_ID, cell_line_name)
dan_test <- dan_test[-which(dan_test$CCLE_Name == ""), ]
old_dan_test <- select(ccl_converter_test, CCLE_Name, Broad_ID, cell_line_name)
old_dan_test <- old_dan_test[-which(old_dan_test$CCLE_Name == ""), ]
colnames(old_dan_test)[colnames(old_dan_test) == "Broad_ID"] <- "Broad_ID_Old"
ccl_test <- select(ccl_info, CCLE_Name, Broad_ID)

test <- merge(ccl_test, dan_test, by = "CCLE_Name", all = TRUE, suffixes = c("_DepMap", "_Daniel"))
test <- merge(test, old_dan_test, by = "CCLE_Name", all = TRUE)
test$BroadIDs_match_Daniel <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Daniel), TRUE, FALSE)
test$BroadIDs_match_Old <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Old), TRUE, FALSE)

test_false_Daniel <- filter(test, BroadIDs_match_Daniel == FALSE)
test_false_Old <- filter(test, BroadIDs_match_Old == FALSE)
# write.table(test_false, file = "~/Desktop/cell_line_database_problems.csv", quote = FALSE, sep = ",")
```

@@

# Whole MAF summary table
maf_summ <- maf_raw[, c("Variant_Classification", "isDeleterious")] %>% group_by(Variant_Classification, isDeleterious) %>% tally()
maf_summ$Percent <- format(round(maf_summ$n / sum(maf_summ$n) * 100, 4), nsmall = 2)
maf_summ$isDeleterious <- ifelse(maf_summ$isDeleterious == "TRUE", "Yes", "No")
knitr::kable(maf_summ, caption = "Distribution of variant classifications in the MAF file") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

>>>>

## D. Charytonowicz cell line converter

This comprehensive cancer cell line information curated by Daniel Charytonowicz.
```{r}
ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180907.tsv", row.names = 1, sep = "\t", header = TRUE)
```

```{r, eval=FALSE, include=FALSE}
# Editing CCL DB
groupings <- read.delim("./data_munging/cell_line_database_completed_extra_grouped_doids_FINAL.csv", sep = "\t", header = TRUE)
groupings <- unique(select(groupings, lineage_name, grouped_general_doid, group_general_lineage_name))

ccl_converter <- read.delim("./data_munging/cell_line_database_FINAL_MASTER.tsv", sep = "\t", row.names = 1, header = TRUE)
colnames(ccl_converter)[colnames(ccl_converter) == "ccle_cell_line_name"] <- "CCLE_Name"
colnames(ccl_converter)[colnames(ccl_converter) == "broad_id"] <- "Broad_ID"

ccl_converter <- merge(ccl_converter, groupings, by = "lineage_name", all.x = TRUE)
```

@@

```{r, include=FALSE}
dan_test <- select(ccl_converter, CCLE_Name, Broad_ID, cell_line_name)
dan_test <- dan_test[-which(dan_test$CCLE_Name == ""), ]
ccl_test <- select(ccl_info, CCLE_Name, Broad_ID)

test <- merge(ccl_test, dan_test, by = "CCLE_Name", all = TRUE, suffixes = c("_DepMap", "_Daniel"))
test$BroadIDs_match <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Daniel), TRUE, FALSE)

test_false <- filter(test, BroadIDs_match == FALSE)
# write.table(ccl_converter, file = "~/Desktop/cell_line_database_v1_20180907.tsv", quote = FALSE, sep = "\t")
```

@@

# Whole MAF summary table
maf_summ <- maf_raw[, c("Variant_Classification", "isDeleterious")] %>% group_by(Variant_Classification, isDeleterious) %>% tally()
maf_summ$Percent <- format(round(maf_summ$n / sum(maf_summ$n) * 100, 4), nsmall = 2)
maf_summ$isDeleterious <- ifelse(maf_summ$isDeleterious == "TRUE", "Yes", "No")

knitr::kable(maf_summ, caption = "Distribution of variant classifications in the MAF file") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

```{r}
max(nchar(as.character(maf_raw$Tumor_Seq_Allele1)))
maf_raw %>% group_by(Variant_Type, isTCGAhotspot) %>% tally()

test <- filter(maf_raw, Hugo_Symbol == "KRAS")
test %>% group_by(isDeleterious) %>% tally()
```
